\begin{samepage}
	\cventry{01/22 - 10/24}
	{Advanced Software Engineer}
	{GDMS (formerly Progeny)}
	{Remote}{} % detail
	{
		% Blank lines not tolerated
		% Company description
		\emph{\\Company Description:}
		%% GDMS
		General Dynamics Mission Systems is an American publicly traded aerospace and
		defense corporation.
		\newline{}
		\newline{}
		% Responsibilities (Single paragraph)
		\emph{Responsibilities:}
		\begin{itemize}
			\item Developed new software components to meet program needs.
			\item Integrated COTS and GOTS tools.
			\item Unit tested software components for integration in larger systems.
			\item Conducted software component integration to ensure end-to-end system functionality.
			\item Researched, identified, and evaluated new technologies for adoption by the US Navy.
			\item Built, integrated, and migrated software applications and components for the community cloud environment.\\
		\end{itemize}
		% Accomplishments (3-5, 2.5 lines each)
		\emph{Accomplishments:}
		\begin{itemize}
			\item Introduced a Hypervisor-based cluster to simulate a full submarine system for end-to-end testing for developers.
			\item Converted the legacy audit system using cloud technologies to improve maintainability and scalability.
			      This allowed the system to handle large bursts (1 GiB/second) of data that were previously unmanageable.
			\item Customized and enhanced a few Red Hat Enterprise Linux (RHEL) based operating systems.\\
		\end{itemize}
		%
		%\textbf{Relevant Skills:} Skill1, Skill2, Skill3, Skill4, Skill5\\
	}
\end{samepage}
